---
title: 'Indian Used Cars Price Prediction - Final Project'
date: '12/1/2020'
output:
  html_document:
    theme: readable
    toc: yes
---

```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
options(scipen = 1, digits = 4, width = 80, fig.align = "center")
```

# Summary Report

## Introduction

### Background

The development speed of India's automobile industry is fast in the world. Due to India's national conditions, poor families account for a large proportion of India. Therefore, because of the price advantage, many people will buy second-hand cars instead of first-hand new cars. This has also promoted the development of the Indian used car market. In India, there are as many as 750 organized used car sales outlets, and this number will continue to grow.

### Our interests
Nowadays, more and more people consider purchasing a used car instead of buying a new one, since it is more feasible and a better investment. However, there are also many frauds and unfair pricing in the market. The most important part of the transaction (buying as well as selling) is making sure the price is fair.

India has a huge market for the used car business. According to the study on the sector, the Indian used car industry possesses significant potential, which was valued at USD 24.24 billion in 2019. Therefore, this dataset should contain much useful information, and be able to help us to construct an efficient model that can predict used/secondhand car prices given some predictor variables. 

### Data File Description
Our dataset focuses on several characteristics of used cars in India. It contains 6018 observations and 13 variables:

1 numeric response variable:

- `Price`: used car prices in INR Lakhs

6 categorical variables:

- `Name`: the car model names
- `Location`: the location of the car sold
- `Fuel_Type`: `Diesel`, `Petrol`, `CNG`
- `Transmission`: `Manual`, `Automatic`
- `Owner_Type`: `First`, `Second`, and some others
- `Seats`: `5`, `7` and some other number of seats

6 numeric variables:

- `Year`: car edition year from 1998 to 2019
- `Kilometers_Driven`: the kilometers already driven of the car in km.
- `Mileage`:  car mileage in kmpl or km/kg
- `Engine`:  the engine volume in cc
- `Power`: the car's power in bhp
- `New Price`: the car price when it's new in INR Lakhs

### Data File Link
The data file can retrived from https://www.kaggle.com/avikasliwal/used-cars-price-prediction?select=train-data.csv as "train-data.csv."

## Import Dataset

```{r}

```

## Introduction (basic information)

```{r}

```

## Data preparation

```{r}

```

## Model establishment and selection

```{r}
#Multiple linear regression, Dummy variables, Interaction, Residual diagnostics, Outlier diagnostics, Transformations, Polynomial regression, Model selection, etc.
```

